SMASH companion source code repository

### 2018-11-08 analysis/index.Rmd
wflow_publish("index.Rmd")
Moved around some files and revised TOC in home page.

[**Illustration:** SMASH applied to the "spikes" data set.](spikesdemo.html)

### Comparisons of signal denoising methods in simulated data

1. [Estimating the mean function from Gaussian-distributed
data.](gausshomo.html)

2. Estimating the variance function from Gaussian-distributed data.

>>>>

### Illustration

+ [SMASH applied to the "Spikes" data set.](spikesdemo.html)

### Simulation experiments

1. [Estimating the mean function from Gaussian-distributed
data.](gaussmeanest.html)

2. [Estimating the variance function from Gaussian-distributed
data](gaussvarest.html).
